---
title: "AIGAN simulation project code for extra datasets"
author: "Yunwei Zhang"
date: “`r paste0('Initiated on 20250704, compiled on ', format(Sys.time(), '%Y %b %d'))`”
output:
  
  html_document:
    code_folding: hide
    fig_height: 8
    fig_width: 12
    highlight: tango
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '4'
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
#usethis::edit_r_environ()
#R_MAX_VSIZE=700Gb
```

This is the code to run statistical simulation and comparison results with ctgan simulated datasets.
This is for regression, binary classification and right censored survival analysis on health and medical datasets.


```{r}
library(Matrix)
library(survival)
library(glmnet)
library(ncvreg)
library(ggplot2)
library(hdnom)
library(Hmisc)
library(survAUC)
library(MASS)
library(tidyverse)
library(purrr)
library(glmnet)
library(modgo)
library(caret)
library(corrplot)
library(reshape2)
```


# Rgression no scale

## stsatitiscal data simulation

```{r }
#testing: need to delete the causing issue if conditions with the "apply" argument
modgo <- function(data,ties_method=  "max", variables= colnames(data),
                  bin_variables= c(),categ_variables= c(),
                  n_samples= nrow(data),sigma= c(),nrep= 100,
                  noise_mu= FALSE, pertr_vec= c(),
                  change_cov= c(),change_amount= 0,seed= 1,
                  thresh_var= c(), thresh_force = FALSE, 
                  var_prop= c(),var_infl=c(),infl_cov_stable=FALSE) {
  
 
  if (!is.na(seed)){
  # Setting Seed
  set.seed(seed)
  
  }

  #Check input  
  
  if (!is.data.frame(data)){
    stop("Data is not a data frame")
  }
  if (any(is.na(data))){
    stop("Data set contains NA's")
  }
  
  if (!all(variables %in% colnames(data))){
  
    stop("Variables are not column names of data ")
  
  }
  
  if (length(sigma)>0 & (colnames(sigma)!= variables ||
                         rownames(sigma)!= variables)){

    stop("Sigma column and row names and not exactly equal to variable names")

  }

  
  # Include only selected variables in the original dataset
  data <- data[,variables]
  
  if(!all(apply(data, 2, function(x) is.numeric(x)))){
    
    stop("Data should only contain numerical values")
    
  }
  if (!all(bin_variables %in% variables)){
  
    stop("Binary variables are not part of the provided variables")
  
  }
  
  # for (bin in bin_variables){
  #   
  #   if(length(which(data[,bin] %in% c(0,1)))<length(data[,bin])) {
  #     
  #     stop(paste0("Binary variable",bin,"is neither 0 nor 1"))
  #     
  #   }
  # }
  # 
  if (!all(categ_variables %in% variables)){
    
    stop("Categorical variables are not part of the provided variables")
    
  }
  
  if (!all(thresh_var[,1] %in% variables)){
    
    stop("Threshold variables are not part of the provided variables")
    
  }
  
  # Find the continuous variables
  continuous_var <- setdiff(variables,c(bin_variables,categ_variables))
  
  if (length(pertr_vec) > 0 && !all(names(pertr_vec) %in% continuous_var) ){
    
    stop("Pertrubation variables are not part of the provided 
         continuous variables")
    
  }
  
  if (length(var_infl) > 0 && !all(names(var_infl) %in% continuous_var) ){
    
    stop("Variance inflation variables are not part of the provided 
         continuous variables")
    
  }
  if (!is.logical(infl_cov_stable)){
    
    stop("Inflation variance stable should be TRUE/FALSE")
    
  }
  
  if(any(names(pertr_vec) %in% names(var_infl))){
    
    stop("Perturb vector cannot have common variables with variance inflation vector")  
    
  }
  
  if (change_amount!=0 && length(change_cov)==0){
    
    stop("You need to provide a pair of variables(change_cov) 
          to change their covariance values")
  }
  
  if (change_amount==0 && length(change_cov)==2){
    
    stop("You need to provide an amount of change (change_amount)")
    
  }
  
  if (!(length(change_cov) %in% c(0,2))) {
    
    stop("You need to provide two variables")
    
  }
  # Noise in multivariate distributions centers
  if (noise_mu == TRUE){
    
    ns <- rnorm(ncol(data),mean = 0,sd=1)
    
    
  } else {
    ns <- matrix(0,nrow = 1,ncol = ncol(data))
    
  }
  
  if (length(var_prop)>0 & !all(names(var_prop) %in% bin_variables)){
    
    stop("Name of var_prop should be a binary variable")
    
  }
  
  if (length(var_prop)>0 & (var_prop>1 || var_prop <0)){
   
     stop("Variable proportion should be between 0 and 1")
    
  }
  
  if (length(var_prop)>1 ){
    
    stop("You cannot set proportion for more than 1 variable")
    
  }
  
  if (length(var_prop) ==1 & length(thresh_var[,1]) >0 ){
   
    stop("You cannot set a variable proportion and 
         a variable threshold at the same run ")
    
  }
  
  OriginalData <- data
  
  # Normal run in case user does not provide a sigma
  if(length(sigma)==0){
    
  # Rank transformation of each column of the data set
  df_rbi <- data
  for(j in 1:ncol(df_rbi)) {
    df_rbi[[j]] <- rbi_normal_transform(data[[j]],ties_method = ties_method)
  }
  Sigma <- cov(df_rbi)
  diag(Sigma) <- 1
  
  categ_var <- c()
  for (ct_var in categ_variables){
    
    if(length(unique(data[,ct_var])) > 7){ 
      print(
      paste0(ct_var,
     " will be treated as continuous due to having more than 7 unique values."))
      }else {
                     categ_var <- c(categ_var,ct_var)
  }
  }
    
  subst_list <- vector(mode="list",length = length(categ_var))
  names(subst_list) <- categ_var
  
  for (cate in categ_var){
    
    unq_values <- sort(unique(data[,cate]))

    values = unq_values
    subst_list[[cate]] <- values
    fake_data <- vector(length = length(data[,cate]))
    
    for (i in c(1:length(unq_values))){
      
      fake_data[which(data[,cate]==values[i])] <- i
      
    } 
    
    data[,cate] <-  fake_data
  }
  
  oldw <- getOption("warn")
  
  options(warn = -1)
  
  
  Sigma <- suppressMessages(Sigma_transformation(
    data=data,data_z = df_rbi,Sigma,
    variables = variables,
    bin_variables = bin_variables,
    categ_variables=categ_var))
 
  options(warn = oldw)
 
  
  
  for (cate in categ_var){
    
    values <- subst_list[[cate]]
    fake_data <- vector(length = length(data[,cate]))
    for (i in c(1:length(values))) {
      
      fake_data[which(data[,cate]==i)] <- values[i]
      
      
      
    }
    data[,cate] <-  fake_data
    
  }
  }else {Sigma <- sigma}
  
# Change specified pairs of covariance matrix by specified amount
 if (change_amount!=0 && length(change_cov)==2) {
   Sigma[change_cov[1],change_cov[2]] <-  
     Sigma[change_cov[2],change_cov[1]] <- 
     Sigma[change_cov[2],change_cov[1]] + change_amount 
   
 }
  
  
  
  # Check Sigma if it is positive definite
  if(!all(eigen(Sigma)$value > 0)){

    print("Covariance matrix is not positive definite.")
    print("It will be replaced with nearest positive definite matrix")
    Sigma <- Matrix::nearPD(Sigma,corr = TRUE)$mat
  }
  
  # Check Sigma if it contains NA's
  if (any(is.na(Sigma))){
    stop("Correlation of data contains NA's")
  }
  
  
  ## Inflation analysis - stable covariance matrix
  if ( length(var_infl) >0 && infl_cov_stable==TRUE){
    
   
    #Inverse transformation of each variable
    for(j in 1:ncol(data)) {
      if(colnames(data)[[j]] %in% names(var_infl)){
        
        p <- var_infl[which(
          names(var_infl)==colnames(data)[[j]])]
        
        data[[j]] <- data[[j]] + 
          rnorm(length(data[[j]]),mean = 0,sd=sd(sqrt(p)*data[[j]]))
        
      }
    }
  }
  
  
  ## Thresholds
  if (length(thresh_var[,1]) >0){
    mt_sim <- MASS::mvrnorm(n = n_samples, 
                            mu = rep(0, ncol(data)) +ns,
                            Sigma = Sigma)
    df_sim <- data.frame(mt_sim)
    names(df_sim) <- names(data)
    #Inverse transformation of each variable
    for(j in 1:ncol(df_sim)) {
      df_sim[[j]] <- rbi_normal_transform_inv(df_sim[[j]], data[[j]])
      
    }
    
    for (i in c(1:length(thresh_var[,1]))){
      if(is.na(thresh_var[i,2]))
      {low_thresh <-
        min(df_sim[thresh_var[i,1]])-1}else{low_thresh <-thresh_var[i,2]}
      if(is.na(thresh_var[i,3]))
      {up_thresh <-
        max(df_sim[thresh_var[i,1]])+1}else{up_thresh <-thresh_var[i,3]}
      
      
      df_sim <- df_sim[which(df_sim[thresh_var[i,1]]< up_thresh &
                               df_sim[thresh_var[i,1]]> low_thresh),]
    }
    
    if(length(df_sim[,1])/n_samples <0.1 & thresh_force == FALSE ){
      stop("The propotion of simulated samples passing
           the threshold is less than 10% ")
    }else if(length(df_sim[,1])==0){
      stop("The propotion of simulated samples passing
           the threshold is 0% ")
    }else{thresh_multi <- 1.1*n_samples/length(df_sim[,1])}
    
    
  }else{thresh_multi=1}
  
  # Binary variables proportions
  if (length(var_prop) ==1 ){
    
    mt_sim <- MASS::mvrnorm(n = n_samples, 
                            mu = rep(0, ncol(data)) +ns,
                            Sigma = Sigma)
    df_sim <- data.frame(mt_sim)
    names(df_sim) <- names(data)
    #Inverse transformation of each variable
    for(j in 1:ncol(df_sim)) {
      df_sim[[j]] <- rbi_normal_transform_inv(df_sim[[j]], data[[j]])
      
    }
    
    counts_1 <- length(which(df_sim[,names(var_prop)]==1))
    counts_0 <- length(which(df_sim[,names(var_prop)]==0))
    req_1 <- var_prop * n_samples
    req_0 <- (1-var_prop) * n_samples
    
    if (req_1 >= counts_1){
      thresh_multi <-  (1.1*req_1)/counts_1
      
    }else if (req_1 < counts_1){
      thresh_multi <-  (1.1*req_0)/counts_0
      
    }
    
    
  }
  
  # Starting loop for many repetions
  
  Correlations <- vector(mode = "list", length = nrep+1)
  mean_corr <- matrix(0,nrow =ncol(data),ncol = ncol(data))
  
  SimulatedData <- vector(mode = "list", length = nrep)
  i <- 1
  counter <- 0
  # Loop for creating new datasets and obtaining their mean correlations
  while (i < nrep+1){
    
  mt_sim <- MASS::mvrnorm(n = ceiling(n_samples*thresh_multi), 
                          mu = rep(0, ncol(data)) + ns,
                          Sigma = Sigma)
  
  
  df_sim <- data.frame(mt_sim)
  names(df_sim) <- names(data)
  #Inverse transformation of each variable
  for(j in 1:ncol(df_sim)) {
    df_sim[[j]] <- rbi_normal_transform_inv(df_sim[[j]], data[[j]])
    
   
    if(colnames(data)[[j]] %in% names(pertr_vec)){
      
      p <- pertr_vec[which(
        names(pertr_vec)==colnames(data)[[j]])]
      
      df_sim[[j]] <- (df_sim[[j]]*sqrt(1-p)) + 
        rnorm(length(df_sim[[j]]),mean = 0,sd=sd(df_sim[[j]])*sqrt(p))
      
    }
    if(colnames(data)[[j]] %in% names(var_infl) && infl_cov_stable == FALSE){
      
      p <- var_infl[which(
        names(var_infl)==colnames(data)[[j]])]
      
      df_sim[[j]] <- df_sim[[j]] + 
       rnorm(length(df_sim[[j]]),mean = 0,sd=sd( sqrt(p)*df_sim[[j]]))
      
    }
  }
  #Threshold process
  if(length(thresh_var[,1])>0){
  for (j in c(1:length(thresh_var[,1]))){
    if(is.na(thresh_var[j,2]))
    {low_thresh <-
      min(df_sim[thresh_var[j,1]])-1}else{low_thresh <-thresh_var[j,2]}
    if(is.na(thresh_var[j,3]))
    {up_thresh <-
      max(df_sim[thresh_var[j,1]])+1}else{up_thresh <-thresh_var[j,3]}
    
    
    df_sim <- df_sim[which(df_sim[thresh_var[j,1]]< up_thresh &
                             df_sim[thresh_var[j,1]]> low_thresh),]
  }
  
  
  }
  #Proportion process
  if(length(var_prop)==1){

      rounded_length <- ceiling(n_samples*var_prop)
      df_sim_1 <- df_sim[which(df_sim[,names(var_prop)] == 1),]
      df_sim_0 <- df_sim[which(df_sim[,names(var_prop)] == 0),]
      df_sim <- rbind(df_sim_1[c(1:rounded_length),],
                      df_sim_0[c(1:(n_samples-rounded_length)),])
      
      
      
      
    
  }
  
  if(length(df_sim[,1]) < n_samples || is.null(df_sim) || any(is.na(suppressWarnings(cor(df_sim)))) ){
    i <- i-1

    counter <-counter +1
  } else {
    df_sim <- df_sim[c(1:n_samples),]
    
    #Correlation calculation
    Correlations[[i]] <- cor(df_sim)
    SimulatedData[[i]] <- df_sim
    
    #Mean correlation calculation
    mean_corr <- mean_corr + (Correlations[[i]]/nrep)
  }
  
  if(counter > 100*nrep){
    stop("Could not create simulated datasets with this specific thresholds")
  } 
  
  i <- i + 1
  }
  
  
  Correlations[[nrep+1]] <- mean_corr
  names(Correlations) <- c(paste0("rep",seq(1:nrep)),"Mean")
  
  results <-list(SimulatedData,OriginalData,Correlations,
                 bin_variables,categ_variables,Sigma,seed,n_samples,nrep)
  names(results) <-c("SimulatedData","OriginalData","Correlations",
                     "Binary_variables","Categorical_variables",
                     "Covariance_Matrix","Seed","Samples_Produced",
                     "Sim_Dataset_Number")
  return(results)
}


Sigma_transformation <- function(data,data_z,Sigma,variables,
                                 bin_variables=c(),categ_variables=c()) {

  cont_variables <- setdiff(variables,c(bin_variables,categ_variables))
  #Binary correlations
  for(bin_var in bin_variables) {
    for(cont_var in cont_variables) {
      invisible(capture.output( aux <- psych::biserial(x = data_z[[cont_var]]
                                                , y = data[[bin_var]])))
      
      Sigma[cont_var, bin_var] <- Sigma[bin_var, cont_var] <- aux
      
    }
    for(cat_variables in categ_variables) {
      invisible(capture.output( aux <- psych::polychoric(
        x = data[, c(cat_variables, bin_var)],global = FALSE)$rho[1, 2]))
      
      Sigma[cat_variables, bin_var] <- Sigma[bin_var, cat_variables] <- aux
      
    }
    for(second_bin_var in bin_variables) {

      if(second_bin_var != bin_var) {
        invisible(capture.output( aux <- psych::tetrachoric(
          x = data[,c(bin_var,second_bin_var)])$rho[1, 2]))
        
        Sigma[second_bin_var, bin_var] <- Sigma[bin_var, second_bin_var] <- aux
      }
    }
  }
  #Categorical correlations
  for(cat_var in categ_variables){
    for(cont_var in cont_variables) {
      invisible(capture.output( aux <- psych::polyserial(x = data_z[[cont_var]],
                                                  y = as.matrix(data[[cat_var]]))))
      
      Sigma[cont_var, cat_var] <- Sigma[cat_var, cont_var] <- aux
      
    }
    for(second_cat_var in categ_variables) {
      if(second_cat_var != cat_var) {
        
        invisible(capture.output( aux <- psych::polychoric(
          x = data[, c(cat_var,second_cat_var)])$rho[1, 2]))
        
        Sigma[second_cat_var, cat_var] <- Sigma[cat_var, second_cat_var] <- aux
      }
    }
  }


return(Sigma)
}
```


# linear regression scaled all

## simulation

```{r}
vitd1=read.csv("bwt.csv")
vitd1=na.omit(vitd1)
covariates=vitd1[,1:2]
covariates<- as.data.frame(apply(covariates, 2, function(x) scale(x)))
vitd1[,1:2]<- covariates
vitd1=vitd1[,c(1:4,9)]
#write_csv(vitd1,"bwt_3_scaled_all.csv")

# # binary: smoke, ht, ui
# # categorical: race, ptl, ftv
# vitd1=read.csv("bwt_3_scaled_all.csv")
# modgo_dt=vitd1[,!colnames(vitd1)=="bwt"]
# binary_variables <- colnames(modgo_dt)[c(4,6,7)]
# categorical_variables <- colnames(modgo_dt)[c(3,5,8)]


#less binary and categorical vars? --works
vitd1=read.csv("bwt_3_scaled_all.csv")
modgo_dt=vitd1[,!colnames(vitd1)%in%c("bwt")]
binary_variables <- colnames(modgo_dt)[4]# binary: smoke
categorical_variables <- colnames(modgo_dt)[3]# categorical: race
# a similar n
test <- modgo(data = modgo_dt,bin_variables = binary_variables,categ_variables = categorical_variables,nrep = 1,ties_method=  "max", variables= colnames(modgo_dt),
                  n_samples= 189,sigma= c(),
                  noise_mu= FALSE, pertr_vec= c(),
                  change_cov= c(),change_amount= 0,seed= 1,
                  thresh_var= c(), thresh_force = FALSE,
                  var_prop= c(),var_infl=c(),infl_cov_stable=FALSE)
modgo_new1=test[[1]][[1]]

#generate output var
formula_str <- paste(colnames(modgo_dt), collapse = " + ")
formula_obj <- as.formula(paste("bwt ~", formula_str))
lm_model <- lm(formula_obj, data = vitd1)
summary(lm_model)
beta <- coef(lm_model)[-1]  # Exclude intercept

# Simulate new data based on the regression model
set.seed(20240421) # Set seed for reproducibility
bwt <- as.matrix(modgo_new1) %*% as.matrix(beta) + rnorm(189,sd = 1)+coef(lm_model)[1] 
vitd1_new1=cbind.data.frame(modgo_new1,bwt)


#write.csv(vitd1_new1,file="bwt_3_stat_scaled_all.csv")
```


## comparison

```{r}
vitd1=read.csv("bwt_3_scaled_all.csv")

vitd1_new1=read.csv("bwt_3_stat_scaled_all.csv")

vitd1_ctgan1=read.csv("bwt_3_sim_scaled_all.csv")

# visualisations
# distribution of covaraite
# Create a data frame with the three vectors
df <- data.frame(value = c(vitd1$age, vitd1_new1$age, vitd1_ctgan1$age),
                 group = c(rep("Real", nrow(vitd1)),rep( "Stat", nrow(vitd1_new1)), rep("CTGAN", nrow(vitd1_ctgan1))))
df$group=factor(df$group, levels=c("Real","CTGAN","Stat"))
# Plot the distribution curves
ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of age", x = "Value", y = "Density") +
  scale_fill_manual(values = c("red", "blue", "green"))+theme_bw()
g1=ggplot(df, aes(x = value, color = group, linetype = group)) +
  geom_density(size = 1) +
  labs(title = "Distribution of age", x = "Value", y = "Density") +
  scale_color_manual(values = c("red", "blue", "green")) +
  theme_bw() 

df <- data.frame(value = c(vitd1$lwt, vitd1_new1$lwt, vitd1_ctgan1$lwt),
                 group = c(rep("Real", nrow(vitd1)),rep( "Stat", nrow(vitd1_new1)), rep("CTGAN", nrow(vitd1_ctgan1))))
df$group=factor(df$group, levels=c("Real","CTGAN","Stat"))
ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of lwt", x = "Value", y = "Density") +
  scale_fill_manual(values = c("red", "blue", "green"))+theme_bw()

g2=ggplot(df, aes(x = value, color = group, linetype = group)) +
  geom_density(size = 1) +
  labs(title = "Distribution of lwt", x = "Value", y = "Density") +
  scale_color_manual(values = c("red", "blue", "green")) +
  theme_bw() 

# distribution of response 
df <- data.frame(value = c(vitd1$bwt, vitd1_new1$bwt, vitd1_ctgan1$bwt),
                 group = c(rep("Real", nrow(vitd1)),rep( "Stat", nrow(vitd1_new1)), rep("CTGAN", nrow(vitd1_ctgan1))))
df$group=factor(df$group, levels=c("Real","CTGAN","Stat"))
ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of bwt", x = "Value", y = "Density") +
  scale_fill_manual(values = c("red", "blue", "green"))+theme_bw()

g3=ggplot(df, aes(x = value, color = group, linetype = group)) +
  geom_density(size = 1) +
  labs(title = "Distribution of bwt", x = "Value", y = "Density") +
  scale_color_manual(values = c("red", "blue", "green")) +
  theme_bw() 

library(gridExtra)
ff=grid.arrange(g1,g2,g3,nrow = 3,ncol=1)
#ggsave(file="bwt_distribution.pdf",ff,height =10 ,width = 5)





# model prediction and feature selection (train on synthtic and evaluation on real)(Brett K Beaulieu-Jones, Zhiwei Steven Wu, Chris Williams, Ran Lee, Sanjeev P Bhavnani,James Brian Byrd, and Casey S Greene. Privacy-preserving generative deep neural networks support clinical data sharing. Circulation: Cardiovascular Quality and Outcomes, 12(7):e005122, 2019.)
train_and_test_lm <- function(train_data, test_data) {
  # Train a linear regression model on the training data
formula_str <- paste(colnames(vitd1_new1)[c(2:5)], collapse = " + ")
formula_obj <- as.formula(paste("bwt ~", formula_str))
lm_model <- lm(formula_obj, data = train_data)

  
  # Make predictions on the test data using the trained model
  test_predictions <- predict(lm_model, newdata = test_data)
  
  # Calculate the mean squared error (MSE) on the test data
  mse <- mean((test_data$bwt - test_predictions)^2,na.rm=TRUE)
  
  # Return the coefficients and MSE
  return(list(coefficients = coef(lm_model), mse = mse))
}

stat_pred=train_and_test_lm(train_data=vitd1_new1,test_data=vitd1)
ctgan_pred=train_and_test_lm(train_data=vitd1_ctgan1,test_data=vitd1)

featuredt=rbind.data.frame(stat_pred$coefficients,ctgan_pred$coefficients)
colnames(featuredt)=names(stat_pred$coefficients)
#featuredt
featuredt$mse=c(stat_pred[[2]],ctgan_pred[[2]])
rownames(featuredt)=c("stat","ctgan")
featuredt
# similarity scores
similarity_metric=function(vec1,vec2){
#KLD:not symmetric, the ref distribution is the second distribution
# Function to compute Kullback-Leibler Divergence (KLD)
KL_divergence <- function(p, q) {
  return(sum(p * log(p / q),na.rm = TRUE))
}

# Compute KLD for the given distributions
KLD <- KL_divergence(vec1, vec2)

# Compute the average inverse of KLD
avg_inv_KLD <- 1 / mean(KLD)


# ks test
ks_result <- ks.test(vec1, vec2)
ks_result$statistic
ks_result$p.value

# chi-squared test: not applicable
# Jensen-Shannon distance (metric) 
# install.packages("philentropy")
# library(divo)
JSD <- function(P, Q) {
  M <- 0.5 * (P + Q)
  #js_divergence <- 0.5 * (KL_divergence(P, M) + KL_divergence(Q, M))
  kl_divergence <- function(P, Q) sum(P * log2(P / Q),na.rm = TRUE)
  js_divergence <- 0.5 * (kl_divergence(P, M) + kl_divergence(Q, M))
  return(sqrt(js_divergence))
}
js_distance <- JSD(vec1, vec2)

#tested the same results
# library(philentropy)
# x=rbind(vec1,vec2)
# philentropy::JSD(x)

# Wasserstein Distance
# install.packages("transport")
# library(transport)
cost_matrix <- outer(vec1, vec2, "-")^2 

wasserstein_distance = purrr::possibly(function(vec1,vec2){return(transport(vec1, vec2, costm = cost_matrix))},
 otherwise = NA)#this gives all for each individual pair
wasserstein_distance2 =wasserstein_distance(vec1,vec2)
#calculate an average
wasserstein_distance_avg=purrr::possibly(function(wasserstein_distance){mean(wasserstein_distance$mass)}, otherwise = NA)
wasserstein_distance_avg2=wasserstein_distance_avg(wasserstein_distance2)

result_vec=c(avg_inv_KLD,as.numeric(ks_result$statistic),js_distance,wasserstein_distance_avg2)
return(result_vec)}


similarity_Calcium=rbind.data.frame(similarity_metric(vec1=vitd1_new1$age,vec2=vitd1$age),similarity_metric(vec1=vitd1_ctgan1$age,vec2=vitd1$age))
colnames(similarity_Calcium)=c("avg_inv_KLD","ks","JS","Wasserstein")
rownames(similarity_Calcium)=c("stat","ctgan")
print("age")
similarity_Calcium
similarity_vitD=rbind.data.frame(similarity_metric(vec1=vitd1_new1$lwt,vec2=vitd1$lwt),similarity_metric(vec1=vitd1_ctgan1$lwt,vec2=vitd1$lwt))
colnames(similarity_vitD)=c("avg_inv_KLD","ks","JS","Wasserstein")
rownames(similarity_vitD)=c("stat","ctgan")
print("lwt")
similarity_vitD
similarity_RIDAGEYR=rbind.data.frame(similarity_metric(vec1=vitd1_new1$bwt,vec2=vitd1$bwt),similarity_metric(vec1=vitd1_ctgan1$bwt,vec2=vitd1$bwt))
colnames(similarity_RIDAGEYR)=c("avg_inv_KLD","ks","JS","Wasserstein")
rownames(similarity_RIDAGEYR)=c("stat","ctgan")
print("bwt")
similarity_RIDAGEYR


#library(writexl)
# List of your data frames
# list_of_dfs <- list(similarity_Calcium = similarity_Calcium, similarity_protein = similarity_protein, similarity_Sodium = similarity_Sodium,similarity_Iron=similarity_Iron,similarity_Glucose_serum=similarity_Glucose_serum,similarity_Creatinine=similarity_Creatinine,similarity_RIDAGEYR=similarity_RIDAGEYR,similarity_vitD=similarity_vitD) 

#write_xlsx(list_of_dfs, "vitd_similarity.xlsx")


get_category_proportions <- function(df,data_name) {
  categorical_cols <- c("race","smoke")
  df[categorical_cols] <- lapply(df[categorical_cols], factor)
  
  # Get names of categorical variables
  cat_vars <- names(df)[sapply(df, is.factor)]
  
  # Create an empty data frame to store proportions
  prop_df <- data.frame(Category = character(), Proportion = numeric(), Data_Frame = character())
  
  # Loop through each categorical variable
  for (var in cat_vars) {
    # Get proportions of categories
    prop <- table(df[[var]]) / length(df[[var]])
    
    # Add proportions to the data frame
    prop_df <- bind_rows(prop_df, data.frame(Category = names(prop), Proportion = prop, Data_Frame = var))
  }
  prop_df=prop_df[,c("Category","Data_Frame","Proportion.Freq")]
  colnames(prop_df)=c("Category","Var","Proportion")
  prop_df$Data=data_name
  return(prop_df)
}

get_category_proportions(vitd1,"real")
get_category_proportions(vitd1_new1,"stat")
get_category_proportions(vitd1_ctgan1,"ctgan")
# Plot
prop_df1 <- get_category_proportions(vitd1,"real")
prop_df2 <- get_category_proportions(vitd1_new1,"stat")
prop_df3 <- get_category_proportions(vitd1_ctgan1,"ctgan")

# Combine proportions from all data frames
combined_prop_df <- bind_rows(prop_df1, prop_df2, prop_df3)

# Plot
ggplot(combined_prop_df, aes(x = Category, y = Proportion, fill = Data)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Category Proportions",
       x = "Category",
       y = "Proportion",
       fill = "Data Frame") +
  theme_minimal()+
  facet_wrap(~ Var, scales = "free")

cat_plot=ggplot(combined_prop_df, aes(x = Category, y = Proportion, fill = Data)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Category Proportions",
       x = "Category",
       y = "Proportion",
       fill = "Data Frame") +
  theme_minimal()+
  facet_wrap(~ Var, scales = "free")

 #ggsave("bwt_cat_prop.pdf",cat_plot,height = 10,width = 15)
# correlation plot
variables=c("age", "lwt" ,"race" , "smoke")
cor1 <- cor(as.matrix(vitd1[,variables]),use = "pairwise.complete.obs")
  cor2 <- cor(as.matrix(vitd1_new1[,variables]),use = "pairwise.complete.obs")
  cor3 <- cor(as.matrix(vitd1_ctgan1[,variables]),use = "pairwise.complete.obs")
 par(mfrow = c(1, 3))
  p1=corrplot::corrplot(cor1,tl.col = "black",col = colorRampPalette(c("blue", "white", "red"))(100))
  p2=corrplot::corrplot(cor2,tl.col = "black",col = colorRampPalette(c("blue", "white", "red"))(100))
  p3=corrplot::corrplot(cor3,tl.col = "black",col = colorRampPalette(c("blue", "white", "red"))(100))
  #save as vitd_correlation
  
  # Melt the correlation matrix
melted_cor_matrix <- melt(cor1)
melted_cor_matrix$shape <- ifelse(melted_cor_matrix$value > 0, "Positive", "Negative")
# Create the plot
g1=ggplot(data = melted_cor_matrix, aes(x = Var1, y = Var2, size = abs(value), shape = shape)) +
  geom_point(color = "black") +
  scale_size(range = c(1, 10),name = "Correlation Value") + # Adjust the size range as needed
  scale_shape_manual(values = c("Positive" = 16, "Negative" = 15)) + # 16 for circle, 15 for square
  theme_minimal() +
  labs(title = "Correlation Heatmap", x = "Variables", y = "Variables", shape = "Correlation Type") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed(ratio = 1)
melted_cor_matrix <- melt(cor2)
melted_cor_matrix$shape <- ifelse(melted_cor_matrix$value > 0, "Positive", "Negative")
# Create the plot
g2=ggplot(data = melted_cor_matrix, aes(x = Var1, y = Var2, size = abs(value), shape = shape)) +
  geom_point(color = "black") +
  scale_size(range = c(1, 10),name = "Correlation Value") + # Adjust the size range as needed
  scale_shape_manual(values = c("Positive" = 16, "Negative" = 15)) + # 16 for circle, 15 for square
  theme_minimal() +
  labs(title = "Correlation Heatmap", x = "Variables", y = "Variables", shape = "Correlation Type") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed(ratio = 1)
melted_cor_matrix <- melt(cor3)
melted_cor_matrix$shape <- ifelse(melted_cor_matrix$value > 0, "Positive", "Negative")
# Create the plot
g3=ggplot(data = melted_cor_matrix, aes(x = Var1, y = Var2, size = abs(value), shape = shape)) +
  geom_point(color = "black") +
  scale_size(range = c(1, 10),name = "Correlation Value") + # Adjust the size range as needed
  scale_shape_manual(values = c("Positive" = 16, "Negative" = 15)) + # 16 for circle, 15 for square
  theme_minimal() +
  labs(title = "Correlation Heatmap", x = "Variables", y = "Variables", shape = "Correlation Type") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed(ratio = 1)
ff=grid.arrange(g1,g2,g3,ncol=3)
  #ggsave("bwt_correlation.pdf",ff,height = 20,width = 20)

   # 2d density plot
  g1=ggplot(vitd1, aes(x = age, y = lwt)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "lwt", title = "Real")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-4,4))+ylim(c(-2,2))
  g2=ggplot(vitd1_new1, aes(x = age, y = lwt)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "lwt", title = "Stat")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-4,4))+ylim(c(-2,2))
  g3=ggplot(vitd1_ctgan1, aes(x = age, y = lwt)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "lwt", title = "CTGAN")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-4,4))+ylim(c(-2,2))
  g4=ggplot(vitd1, aes(x = age, y = bwt)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "bwt", title = "Real")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(0,5000))
  g5=ggplot(vitd1_new1, aes(x = age, y = bwt)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "bwt", title = "Stat")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(0,5000))
  g6=ggplot(vitd1_ctgan1, aes(x = age, y = bwt)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "bwt", title = "CTGAN")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(0,5000))
  g7=ggplot(vitd1, aes(x = bwt, y = smoke)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "bwt", y = "smoke", title = "Real")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(0,5000))+ylim(c(0,1))
  g8=ggplot(vitd1_new1, aes(x = bwt, y = smoke)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "bwt", y = "smoke", title = "Stat")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(0,5000))+ylim(c(0,1))
  g9=ggplot(vitd1_ctgan1, aes(x = bwt, y = smoke)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "bwt", y = "smoke", title = "CTGAN")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(0,5000))+ylim(c(0,1))
  
  ff=grid.arrange(g1,g2,g3,g4,g5,g6,g7,g8,g9,ncol=3)
  #ggsave("2d_density_bwt.pdf",ff,height = 10,width = 10)
```



# binary classification heart

## binary classification simulation

### all variables

```{r}
heartdt=read.csv("breast3.csv")
modgo_dt=heartdt[,!colnames(heartdt)=="outcome"]
colnames(modgo_dt)
modgo_dt=as.data.frame(modgo_dt)
#modgo_dt$sex=as.integer(modgo_dt$sex)
binary_variables <- c()
categorical_variables <- c()
test <- modgo(data = modgo_dt,bin_variables = binary_variables,categ_variables = categorical_variables,nrep = 1,ties_method=  "max", variables= colnames(modgo_dt),
                  n_samples= 569,sigma= c(),
                  noise_mu= FALSE, pertr_vec= c(),
                  change_cov= c(),change_amount= 0,seed= 1,
                  thresh_var= c(), thresh_force = FALSE,
                  var_prop= c(),var_infl=c(),infl_cov_stable=FALSE)
modgo_new1=test[[1]][[1]]

#generate output var
formula_str <- paste(paste(colnames(modgo_dt), collapse = " + "), "1", sep = "-")
formula_obj <- as.formula(paste("outcome ~", formula_str))
lm_model <- glm(formula_obj, data = heartdt, family=binomial())
summary(lm_model)

# Simulate new data based on the regression model
set.seed(20240421) # Set seed for reproducibility
probs<- predict(lm_model, newdata = as.data.frame(modgo_new1), type = "response")
outcome <- rbinom(n = 569, size = 1, prob = probs)
vitd1_new1=cbind.data.frame(modgo_new1,outcome)


#write_csv(vitd1_new1,file="breast_3_stat.csv")
```


## binary classification comparison


```{r }
vitd1=read.csv("breast3.csv")
vitd1_new1=read.csv("breast_3_stat.csv")
vitd1_ctgan1=read.csv("breast3_sim1.csv")

#  V1-V31


# visualisations
# distribution of covaraite
# Create a data frame with the three vectors
df <- data.frame(value = c(vitd1$V3, vitd1_new1$V3, vitd1_ctgan1$V3),
                 group = c(rep("Real", nrow(vitd1)),rep( "Stat", nrow(vitd1_new1)), rep("CTGAN", nrow(vitd1_ctgan1))))

# Plot the distribution curves
ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of V3", x = "Value", y = "Density") +
  scale_fill_manual(values = c("blue", "red", "green"))+theme_bw()
g1=ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of V3", x = "Value", y = "Density") +
  scale_fill_manual(values = c("blue", "red", "green"))+theme_bw()
df <- data.frame(value = c(vitd1$V31, vitd1_new1$V31, vitd1_ctgan1$V31),
                 group = c(rep("Real", nrow(vitd1)),rep( "Stat", nrow(vitd1_new1)), rep("CTGAN", nrow(vitd1_ctgan1))))

# Plot the distribution curves
ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of V31", x = "Value", y = "Density") +
  scale_fill_manual(values = c("blue", "red", "green"))+theme_bw()
g2=ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of V31", x = "Value", y = "Density") +
  scale_fill_manual(values = c("blue", "red", "green"))+theme_bw()
df <- data.frame(value = c(vitd1$V10, vitd1_new1$V10, vitd1_ctgan1$V10),
                 group = c(rep("Real", nrow(vitd1)),rep( "Stat", nrow(vitd1_new1)), rep("CTGAN", nrow(vitd1_ctgan1))))

# Plot the distribution curves
ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of V10", x = "Value", y = "Density") +
  scale_fill_manual(values = c("blue", "red", "green"))+theme_bw()
g3=ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of V10", x = "Value", y = "Density") +
  scale_fill_manual(values = c("blue", "red", "green"))+theme_bw()
ff=grid.arrange(g1,g2,g3,ncol=1)
#ggsave("breast_distribution.pdf",ff,height = 10,width = 5)

# distribution of response 
# Create frequency tables
freq_df1 <- table(vitd1$outcome) %>% prop.table()%>% as.data.frame() %>% rename(target = Var1, Count = Freq)
freq_df1$Dataset <- "Real"
freq_df2 <- table(vitd1_new1$outcome) %>% prop.table()%>% as.data.frame() %>% rename(target = Var1, Count = Freq)
freq_df2$Dataset <- "Stat"
freq_df3 <- table(vitd1_ctgan1$outcome) %>% prop.table()%>% as.data.frame() %>% rename(target = Var1, Count = Freq)
freq_df3$Dataset <- "CTGAN"

# Combine the frequency tables
combined_df <- rbind(freq_df1, freq_df2,freq_df3)

# Plotting
ggplot(combined_df, aes(x = target, y = Count, fill = Dataset)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of outcome by Dataset",
       x = "outcome",
       y = "Count",
       fill = "Dataset") +
  theme_minimal()


# model prediction and feature selection (train on synthtic and evaluation on real)(Brett K Beaulieu-Jones, Zhiwei Steven Wu, Chris Williams, Ran Lee, Sanjeev P Bhavnani,James Brian Byrd, and Casey S Greene. Privacy-preserving generative deep neural networks support clinical data sharing. Circulation: Cardiovascular Quality and Outcomes, 12(7):e005122, 2019.)
train_and_test_glm <- function(train_data, test_data) {
  # Train a linear regression model on the training data
formula_str <- paste(colnames(vitd1)[2:31], collapse = " + ")
formula_obj <- as.formula(paste("outcome ~", formula_str))
lm_model <- glm(formula_obj, data = train_data,family = binomial())

  
  # Make predictions on the test data using the trained model
  test_predictions <- predict(lm_model, newdata = test_data,type = "response")
  
  # Calculate the accuracy on the test data
  predicted_classes <- ifelse(test_predictions > quantile(test_predictions)[3], 1, 0)

# Create confusion matrix
  actual=factor(test_data$outcome,levels = c(0,1))
  predicted=factor(predicted_classes,levels = c(0,1))
conf_matrix <- confusionMatrix(actual, predicted)

# Calculate balanced accuracy
balanced_accuracy <- conf_matrix$byClass["Balanced Accuracy"]

TP <- conf_matrix$table[2,2]  # True Positive
FP <- conf_matrix$table[1,2]  # False Positive
FN <- conf_matrix$table[2,1]  # False Negative

# Calculate precision and recall
precision <- TP / (TP + FP)
recall <- TP / (TP + FN)

# Calculate F1 score
F1 <- 2 * precision * recall / (precision + recall)

  # Return the coefficients and MSE
  return(list(coefficients = coef(lm_model), accuracy = balanced_accuracy,f1=F1))
}

stat_pred=train_and_test_glm(train_data=vitd1_new1,test_data=vitd1)
ctgan_pred=train_and_test_glm(train_data=vitd1_ctgan1,test_data=vitd1)

featuredt=rbind.data.frame(stat_pred$coefficients,ctgan_pred$coefficients)
colnames(featuredt)=names(stat_pred$coefficients)
#featuredt
featuredt$accuracy=c(stat_pred[[2]],ctgan_pred[[2]])
featuredt$f1=c(stat_pred[[3]],ctgan_pred[[3]])
rownames(featuredt)=c("stat","ctgan")
featuredt

# sanity checks (https://github.com/vanderschaarlab/synthcity)(not in the paper, decided not doing here)
# also, the privacy related metrics are not used here

similarity_age=rbind.data.frame(similarity_metric(vec1=vitd1_new1$V3,vec2=vitd1$V3),similarity_metric(vec1=vitd1_ctgan1$V3,vec2=vitd1$V3))
colnames(similarity_age)=c("avg_inv_KLD","ks","JS","Wasserstein")
rownames(similarity_age)=c("stat","ctgan")
print("similarity_age")
similarity_age
similarity_target=rbind.data.frame(similarity_metric(vec1=vitd1_new1$outcome,vec2=vitd1$outcome),similarity_metric(vec1=vitd1_ctgan1$outcome,vec2=vitd1$outcome))
colnames(similarity_target)=c("avg_inv_KLD","ks","JS","Wasserstein")
rownames(similarity_target)=c("stat","ctgan")
print("similarity_target")
similarity_target


# Function to calculate similarity metrics for all columns in the datasets
calculate_similarity_for_all_columns <- function(dataset1, dataset2,dataset3) {
  result_list <- list()
  for (col in names(dataset1)) {
    similarity_df <- rbind.data.frame(similarity_metric(vec1=dataset2[[col]],vec2=dataset1[[col]]),similarity_metric(vec1=dataset3[[col]],vec2=dataset1[[col]]))
    colnames(similarity_df)=c("avg_inv_KLD","ks","JS","Wasserstein")
rownames(similarity_df)=c("stat","ctgan")
    result_list[[col]] <- similarity_df
  }
  return(result_list)
}

# Call the function to get similarity results for all columns
similarity_results <- calculate_similarity_for_all_columns(vitd1,vitd1_new1,vitd1_ctgan1)

#write_xlsx(similarity_results, "heart_similarity.xlsx")

# # categorical variables plot
# get_category_proportions <- function(df,data_name) {
#   categorical_cols <- colnames(vitd1)[c(2,6,7,9,11,13)]
#   df[categorical_cols] <- lapply(df[categorical_cols], factor)
#   
#   # Get names of categorical variables
#   cat_vars <- names(df)[sapply(df, is.factor)]
#   
#   # Create an empty data frame to store proportions
#   prop_df <- data.frame(Category = character(), Proportion = numeric(), Data_Frame = character())
#   
#   # Loop through each categorical variable
#   for (var in cat_vars) {
#     # Get proportions of categories
#     prop <- table(df[[var]]) / length(df[[var]])
#     
#     # Add proportions to the data frame
#     prop_df <- bind_rows(prop_df, data.frame(Category = names(prop), Proportion = prop, Data_Frame = var))
#   }
#   prop_df=prop_df[,c("Category","Data_Frame","Proportion.Freq")]
#   colnames(prop_df)=c("Category","Var","Proportion")
#   prop_df$Data=data_name
#   return(prop_df)
# }
# 
# get_category_proportions(vitd1,"real")
# get_category_proportions(vitd1_new1,"stat")
# get_category_proportions(vitd1_ctgan1,"ctgan")
# 
# # Plot
# prop_df1 <- get_category_proportions(vitd1,"real")
# prop_df2 <- get_category_proportions(vitd1_new1,"stat")
# prop_df3 <- get_category_proportions(vitd1_ctgan1,"ctgan")
# 
# # Combine proportions from all data frames
# combined_prop_df <- bind_rows(prop_df1, prop_df2, prop_df3)
# 
# # Plot
# ggplot(combined_prop_df, aes(x = Category, y = Proportion, fill = Data)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   labs(title = "Comparison of Category Proportions",
#        x = "Category",
#        y = "Proportion",
#        fill = "Data Frame") +
#   theme_minimal()+
#   facet_wrap(~ Var, scales = "free")
# 
# cat_prop=ggplot(combined_prop_df, aes(x = Category, y = Proportion, fill = Data)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   labs(title = "Comparison of Category Proportions",
#        x = "Category",
#        y = "Proportion",
#        fill = "Data Frame") +
#   theme_minimal()+
#   facet_wrap(~ Var, scales = "free")
# 
# #ggsave("heart_cat_prop.pdf",cat_prop,height = 10,width = 15)
# correlation plot
variables=colnames(vitd1)[2:31]
cor1 <- cor(as.matrix(vitd1[,variables]),use = "pairwise.complete.obs")
  cor2 <- cor(as.matrix(vitd1_new1[,variables]),use = "pairwise.complete.obs")
  cor3 <- cor(as.matrix(vitd1_ctgan1[,variables]),use = "pairwise.complete.obs")
 par(mfrow = c(1, 3))
  p1=corrplot::corrplot(cor1,tl.col = "black",col = colorRampPalette(c("blue", "white", "red"))(100))
  p2=corrplot::corrplot(cor2,tl.col = "black",col = colorRampPalette(c("blue", "white", "red"))(100))
  p3=corrplot::corrplot(cor3,tl.col = "black",col = colorRampPalette(c("blue", "white", "red"))(100))
#save as heart_correlation
  
    # Melt the correlation matrix
melted_cor_matrix <- melt(cor1)
melted_cor_matrix$shape <- ifelse(melted_cor_matrix$value > 0, "Positive", "Negative")
# Create the plot
g1=ggplot(data = melted_cor_matrix, aes(x = Var1, y = Var2, size = abs(value), shape = shape)) +
  geom_point(color = "black") +
  scale_size(range = c(1, 10),name = "Correlation Value") + # Adjust the size range as needed
  scale_shape_manual(values = c("Positive" = 16, "Negative" = 15)) + # 16 for circle, 15 for square
  theme_minimal() +
  labs(title = "Correlation Heatmap", x = "Variables", y = "Variables", shape = "Correlation Type") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed(ratio = 1)
melted_cor_matrix <- melt(cor2)
melted_cor_matrix$shape <- ifelse(melted_cor_matrix$value > 0, "Positive", "Negative")
# Create the plot
g2=ggplot(data = melted_cor_matrix, aes(x = Var1, y = Var2, size = abs(value), shape = shape)) +
  geom_point(color = "black") +
  scale_size(range = c(1, 10),name = "Correlation Value") + # Adjust the size range as needed
  scale_shape_manual(values = c("Positive" = 16, "Negative" = 15)) + # 16 for circle, 15 for square
  theme_minimal() +
  labs(title = "Correlation Heatmap", x = "Variables", y = "Variables", shape = "Correlation Type") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed(ratio = 1)
melted_cor_matrix <- melt(cor3)
melted_cor_matrix$shape <- ifelse(melted_cor_matrix$value > 0, "Positive", "Negative")
# Create the plot
g3=ggplot(data = melted_cor_matrix, aes(x = Var1, y = Var2, size = abs(value), shape = shape)) +
  geom_point(color = "black") +
  scale_size(range = c(1, 10),name = "Correlation Value") + # Adjust the size range as needed
  scale_shape_manual(values = c("Positive" = 16, "Negative" = 15)) + # 16 for circle, 15 for square
  theme_minimal() +
  labs(title = "Correlation Heatmap", x = "Variables", y = "Variables", shape = "Correlation Type") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed(ratio = 1)
ff=grid.arrange(g1,g2,g3,ncol=3)
  #ggsave("breast_correlation.pdf",ff,height = 20,width = 20)

  # 2d density plot
  g1=ggplot(vitd1, aes(x = V3, y = V5)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "V3", y = "V5", title = "Real")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(-3,3))
  g2=ggplot(vitd1_new1, aes(x = V3, y = V5)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "V3", y = "V5", title = "Stat")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(-3,3))
  g3=ggplot(vitd1_ctgan1, aes(x = V3, y = V5)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "V3", y = "V5", title = "CTGAN")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(-3,3))
  g4=ggplot(vitd1, aes(x = outcome, y = V3)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "outcome", y = "V3", title = "Real")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(0,1))+ylim(c(0,1))
  g5=ggplot(vitd1_new1, aes(x = outcome, y = V3)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "outcome", y = "V3", title = "Stat")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(0,1))+ylim(c(0,1))
  g6=ggplot(vitd1_ctgan1, aes(x = outcome, y = V3)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "outcome", y = "V3", title = "CTGAN")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(0,1))+ylim(c(0,1))
  g7=ggplot(vitd1, aes(x = V10, y = V31)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "V10", y = "V31", title = "Real")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(0,1))
  g8=ggplot(vitd1_new1, aes(x = V10, y = V31)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "V10", y = "V31", title = "Stat")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(0,1))
  g9=ggplot(vitd1_ctgan1, aes(x = V10, y = V31)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "V10", y = "V31", title = "CTGAN")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(0,1))
  
   
  ff=grid.arrange(g1,g2,g3,g7,g8,g9,g4,g5,g6,ncol=3)
  #ggsave("2d_density_breast.pdf",ff,height = 10,width = 10)
```


# survival

## survival simulation

```{r}
sim_fun_cox=function(dat,seed,n,X){
cov_names=colnames(dat)[which(!colnames(dat)%in%c("time","status"))]
est.model=coxph(as.formula(paste("Surv(time,status)~", paste(cov_names, collapse="+"))),data=dat)
      haz <- basehaz(est.model)
      # any(is.na(haz))
      # any(is.infinite(haz$hazard))
      # any(is.infinite(haz$time))
      # any(is.nan(haz$hazard))
      # any(is.nan(haz$time))
      # class(haz$hazard)
      # class(haz$time)
      haz=as.data.frame(haz)
      dim(haz)
      haz.new=haz[haz$hazard>0&haz$time>0,]
      bhaz.model <- lm(log(hazard)~log(time),data=haz.new)
      shape.init <- bhaz.model$coef[2]
      scale.init <- exp(bhaz.model$coef[1]/bhaz.model$coef[2])
      k.shape<-shape.init
      h0=scale.init

  set.seed(seed)
  r.u <- runif(n)
  beta=as.matrix(est.model$coefficients)
  ftime <- (-log(r.u)/((h0^k.shape)*exp(as.matrix(X) %*% beta)))^(1/k.shape)
  ctime=runif(n,min=0,max=1000)
  time <- pmin(ftime, ctime)
  status <- as.numeric(ftime <= ctime)
  current_data2=cbind.data.frame(time,status,X)
  return(current_data2)
}

```

## survival comparison


```{r}
vitd1=read.csv("lung3.csv")
vitd1_new1=read.csv("lung3_stat.csv")
vitd1_ctgan1=read.csv("lung3_sim1.csv")


# visualisations
# distribution of covaraite
# Create a data frame with the three vectors
df <- data.frame(value = c(vitd1$age, vitd1_new1$age, vitd1_ctgan1$age),
                 group = c(rep("Real", nrow(vitd1)),rep( "Stat", nrow(vitd1_new1)), rep("CTGAN", nrow(vitd1_ctgan1))))

# Plot the distribution curves
ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of age", x = "Value", y = "Density") +
  scale_fill_manual(values = c("blue", "red", "green"))+theme_bw()

df <- data.frame(value = c(vitd1$time, vitd1_new1$time, vitd1_ctgan1$time),
                 group = c(rep("Real", nrow(vitd1)),rep( "Stat", nrow(vitd1_new1)), rep("CTGAN", nrow(vitd1_ctgan1))))

# Plot the distribution curves
ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.3) +
  labs(title = "Distribution of time", x = "Value", y = "Density") +
  scale_fill_manual(values = c("blue", "red", "green"))+theme_bw()

# distribution of response 
# Create frequency tables
freq_df1 <- table(vitd1$status) %>% prop.table()%>% as.data.frame() %>% rename(status = Var1, Count = Freq)
freq_df1$Dataset <- "Real"
freq_df2 <- table(vitd1_new1$status) %>% prop.table()%>% as.data.frame() %>% rename(status = Var1, Count = Freq)
freq_df2$Dataset <- "Stat"
freq_df3 <- table(vitd1_ctgan1$status) %>% prop.table()%>% as.data.frame() %>% rename(status = Var1, Count = Freq)
freq_df3$Dataset <- "CTGAN"

# Combine the frequency tables
combined_df <- rbind(freq_df1, freq_df2,freq_df3)
combined_df
# Plotting
ggplot(combined_df, aes(x = status, y = Count, fill = Dataset)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of status by Dataset",
       x = "status",
       y = "Count",
       fill = "Dataset") +
  theme_minimal()

similarity_age=rbind.data.frame(similarity_metric(vec1=vitd1_new1$age,vec2=vitd1$age),similarity_metric(vec1=vitd1_ctgan1$age,vec2=vitd1$age))
colnames(similarity_age)=c("avg_inv_KLD","ks","JS","Wasserstein")
rownames(similarity_age)=c("stat","ctgan")
print("similarity_age")
similarity_age
# Call the function to get similarity results for all columns
similarity_results <- calculate_similarity_for_all_columns(vitd1,vitd1_new1,vitd1_ctgan1)

#write_xlsx(similarity_results, "veteran_similarity.xlsx")
# model prediction and feature selection (train on synthtic and evaluation on real)(Brett K Beaulieu-Jones, Zhiwei Steven Wu, Chris Williams, Ran Lee, Sanjeev P Bhavnani,James Brian Byrd, and Casey S Greene. Privacy-preserving generative deep neural networks support clinical data sharing. Circulation: Cardiovascular Quality and Outcomes, 12(7):e005122, 2019.)
train_and_test_cox <- function(train_data, test_data) {
  # Train a linear regression model on the training data
formula_str <- paste(colnames(vitd1)[3:9], collapse = " + ")
formula_obj <- as.formula(paste("Surv(time,status) ~", formula_str))
coxmod <- coxph(formula_obj,x=TRUE, data = train_data)
predd<-predict(object=coxmod,newdata=test_data,type="risk")
  harrelC1 <- Hmisc::rcorr.cens(-predd,with(test_data,survival::Surv(time,status)))
  hc<-harrelC1["C Index"]
  lp<- predict(coxmod)
    lpnew <- predict(coxmod, newdata=test_data)
    Surv.rsp <- survival::Surv(train_data$time, train_data$status)
    Surv.rsp.new <- survival::Surv(test_data$time, test_data$status)
  briers1 <- survAUC::predErr(Surv.rsp, Surv.rsp.new, lp, lpnew,times=test_data$time, type = "brier", int.type = "unweighted")$error
  briers1_without_inf <- briers1[is.finite(briers1)]
  bs<-sum(na.omit(briers1_without_inf))
  
  # ibsfun1=purrr::possibly(function(modell){
  #     briers3 <- pec::pec(list("cox1"=modell),data=test_data,formula=formula_obj,cens.model="cox")
  #     return(crps(briers3)[2])
  #   },otherwise = NA)
  #   bs3<-ibsfun1(coxmod)
    
  # Return the coefficients and MSE
  return(list(coefficients = coef(coxmod), cindex = hc,Brier_score=bs))
}

stat_pred=train_and_test_cox(train_data=vitd1_new1,test_data=vitd1)
ctgan_pred=train_and_test_cox(train_data=vitd1_ctgan1,test_data=vitd1)

featuredt=rbind.data.frame(stat_pred$coefficients,ctgan_pred$coefficients)
colnames(featuredt)=names(stat_pred$coefficients)
#featuredt
featuredt$cindex=c(stat_pred[[2]],ctgan_pred[[2]])
featuredt$bs=c(stat_pred[[3]],ctgan_pred[[3]])
rownames(featuredt)=c("stat","ctgan")
featuredt

# categorical variables plot


get_category_proportions <- function(df,data_name) {
  categorical_cols <- colnames(vitd1)[c(4,5)]
  df[categorical_cols] <- lapply(df[categorical_cols], factor)
  
  # Get names of categorical variables
  cat_vars <- names(df)[sapply(df, is.factor)]
  
  # Create an empty data frame to store proportions
  prop_df <- data.frame(Category = character(), Proportion = numeric(), Data_Frame = character())
  
  # Loop through each categorical variable
  for (var in cat_vars) {
    # Get proportions of categories
    prop <- table(df[[var]]) / length(df[[var]])
    
    # Add proportions to the data frame
    prop_df <- bind_rows(prop_df, data.frame(Category = names(prop), Proportion = prop, Data_Frame = var))
  }
  prop_df=prop_df[,c("Category","Data_Frame","Proportion.Freq")]
  colnames(prop_df)=c("Category","Var","Proportion")
  prop_df$Data=data_name
  return(prop_df)
}

get_category_proportions(vitd1,"real")
get_category_proportions(vitd1_new1,"stat")
get_category_proportions(vitd1_ctgan1,"ctgan")
# Plot
prop_df1 <- get_category_proportions(vitd1,"real")
prop_df2 <- get_category_proportions(vitd1_new1,"stat")
prop_df3 <- get_category_proportions(vitd1_ctgan1,"ctgan")

# Combine proportions from all data frames
combined_prop_df <- bind_rows(prop_df1, prop_df2, prop_df3)

# Plot
ggplot(combined_prop_df, aes(x = Category, y = Proportion, fill = Data)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Category Proportions",
       x = "Category",
       y = "Proportion",
       fill = "Data Frame") +
  theme_minimal()+
  facet_wrap(~ Var, scales = "free")
cat_plot=ggplot(combined_prop_df, aes(x = Category, y = Proportion, fill = Data)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Category Proportions",
       x = "Category",
       y = "Proportion",
       fill = "Data Frame") +
  theme_minimal()+
  facet_wrap(~ Var, scales = "free")
cat_plot=ggplot(combined_prop_df, aes(x = Category, y = Proportion, fill = Data)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Category Proportions",
       x = "Category",
       y = "Proportion",
       fill = "Data Frame") +
  theme_minimal()+
  facet_wrap(~ Var, scales = "free")

#ggsave("lung_cat_prop.pdf",cat_plot,height=5,width = 10)
variables=c("age","sex" ,"ph.ecog", "ph.karno","pat.karno","meal.cal","wt.loss")
cor1 <- cor(as.matrix(vitd1[,variables]),use = "pairwise.complete.obs")
  cor2 <- cor(as.matrix(vitd1_new1[,variables]),use = "pairwise.complete.obs")
  cor3 <- cor(as.matrix(vitd1_ctgan1[,variables]),use = "pairwise.complete.obs")
 par(mfrow = c(1, 3))
  p1=corrplot::corrplot(cor1,tl.col = "black",col = colorRampPalette(c("blue", "white", "red"))(100))
  p2=corrplot::corrplot(cor2,tl.col = "black",col = colorRampPalette(c("blue", "white", "red"))(100))
  p3=corrplot::corrplot(cor3,tl.col = "black",col = colorRampPalette(c("blue", "white", "red"))(100))
  
  #save as veteran_correlation
    # Melt the correlation matrix
melted_cor_matrix <- melt(cor1)
melted_cor_matrix$shape <- ifelse(melted_cor_matrix$value > 0, "Positive", "Negative")
# Create the plot
g1=ggplot(data = melted_cor_matrix, aes(x = Var1, y = Var2, size = abs(value), shape = shape)) +
  geom_point(color = "black") +
  scale_size(range = c(1, 10),name = "Correlation Value") + # Adjust the size range as needed
  scale_shape_manual(values = c("Positive" = 16, "Negative" = 15)) + # 16 for circle, 15 for square
  theme_minimal() +
  labs(title = "Correlation Heatmap", x = "Variables", y = "Variables", shape = "Correlation Type") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed(ratio = 1)
melted_cor_matrix <- melt(cor2)
melted_cor_matrix$shape <- ifelse(melted_cor_matrix$value > 0, "Positive", "Negative")
# Create the plot
g2=ggplot(data = melted_cor_matrix, aes(x = Var1, y = Var2, size = abs(value), shape = shape)) +
  geom_point(color = "black") +
  scale_size(range = c(1, 10),name = "Correlation Value") + # Adjust the size range as needed
  scale_shape_manual(values = c("Positive" = 16, "Negative" = 15)) + # 16 for circle, 15 for square
  theme_minimal() +
  labs(title = "Correlation Heatmap", x = "Variables", y = "Variables", shape = "Correlation Type") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed(ratio = 1)
melted_cor_matrix <- melt(cor3)
melted_cor_matrix$shape <- ifelse(melted_cor_matrix$value > 0, "Positive", "Negative")
# Create the plot
g3=ggplot(data = melted_cor_matrix, aes(x = Var1, y = Var2, size = abs(value), shape = shape)) +
  geom_point(color = "black") +
  scale_size(range = c(1, 10),name = "Correlation Value") + # Adjust the size range as needed
  scale_shape_manual(values = c("Positive" = 16, "Negative" = 15)) + # 16 for circle, 15 for square
  theme_minimal() +
  labs(title = "Correlation Heatmap", x = "Variables", y = "Variables", shape = "Correlation Type") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  coord_fixed(ratio = 1)
ff=grid.arrange(g1,g2,g3,ncol=3)
  #ggsave("lung_correlation.pdf",ff,height = 20,width = 20)

   # 2d density plot
  g1=ggplot(vitd1, aes(x = age, y = sex)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "sex", title = "Real")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(0,1))
  g2=ggplot(vitd1_new1, aes(x = age, y = sex)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "sex", title = "Stat")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(0,1))
  g3=ggplot(vitd1_ctgan1, aes(x = age, y = sex)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "sex", title = "CTGAN")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(0,1))
 
   g4=ggplot(vitd1, aes(x = age, y = wt.loss)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "wt.loss", title = "Real")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(-3,3))
  g5=ggplot(vitd1_new1, aes(x = age, y = wt.loss)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "wt.loss", title = "Stat")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(-3,3))
  g6=ggplot(vitd1_ctgan1, aes(x = age, y = wt.loss)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "age", y = "wt.loss", title = "CTGAN")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-3,3))+ylim(c(-3,3))
  
  g7=ggplot(vitd1, aes(x = meal.cal, y = wt.loss)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "meal.cal", y = "wt.loss", title = "Real")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-4,4))+ylim(c(-3,3))
  g8=ggplot(vitd1_new1, aes(x = meal.cal, y = wt.loss)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "meal.cal", y = "wt.loss", title = "Stat")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-4,4))+ylim(c(-3,3))
  g9=ggplot(vitd1_ctgan1, aes(x = meal.cal, y = wt.loss)) +
  geom_density_2d(aes(color = ..level..), bins = 50, bw = 0.1) +geom_point(alpha = 0.3,size=0.3)+
  labs(x = "meal.cal", y = "wt.loss", title = "CTGAN")+theme_bw()+theme(aspect.ratio = 1)+scale_color_gradient(low = "lightblue", high = "darkblue", limits = c(0, 0.2))+xlim(c(-4,4))+ylim(c(-3,3))
  
   
 
  ff=grid.arrange(g1,g2,g3,g4,g5,g6,g7,g8,g9,ncol=3)
  #ggsave("2d_density_lung.pdf",ff,height = 15,width = 10)
```


